---
title: "Calibrating Snow Gauge"
author: "Iza"
date: "3/24/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## the data
```{r}
Density = c(0.686,0.604,0.508,0.412,
            0.318,0.223,0.148,0.080,0.001)

Gain1 = c(17.6,24.8,39.4,60.0,
          87.0,128,199,298,423)
Gain2 = c(17.3,25.9,37.6,58.3,
          92.7,130,204,298,421)
Gain3 = c(16.9,26.3,38.1,59.6,
          90.5,131,199,297,422)
Gain4 = c(16.2,24.8,37.7,59.1,
          85.8,129,207,288,428)
Gain5 = c(17.1,24.8,36.3,56.3,
          87.5,127,200,296,436)
Gain6 = c(18.5,27.6,38.7,55.0,
          88.3,129,200,293,427)
Gain7 = c(18.7,28.5,39.4,52.9,
          91.6,132,205,301,426)
Gain8 = c(17.4,30.5,38.8,54.1,
          88.2,133,202,299,428)
Gain9 = c(18.6,28.4,39.2,56.9,
          88.6,134,199,298,427)
Gain10 = c(16.8,27.7,40.3,56.0,
           84.7,133,199,293,429)

#df with only two columns
df1 = data.frame(
  rep(Density,10),
  c(Gain1,Gain2,Gain3,Gain4,Gain5,
    Gain6,Gain7,Gain8,Gain9,Gain10))
#chage column names
names(df1) = c("Density","Gain")

```

## How are density and gain related?
```{r}
library(ggplot2)

dxg = ggplot(df1,aes(x=Density, y =Gain))
dxg_df1 = dxg + ggtitle("Point Plot each Polyethylene Density and its 10 Gains reading") + geom_point(aes(colour = factor(Density)))
```

# Relationship of Gain and Density
$Gain = e^{b*Density}$ or $ln(Gain) = b*Density$


# model 0: just a linear 
```{r}
model0 = lm(Gain~Density, data=df1)
summary(model0)
coefs1 = model0$coefficients
plot(model0)
```



# Model fitting using trasformation and linear regression
In order to use "lm()" we have to make the relationship between the two variables to be linear. Hence the log transformation of the Gain variable.
```{r}
model1 = lm(log(Gain)~Density, data=df1)
summary(model1)
coefs1 = model1$coefficients
plot(model1)
```

# the physical model representin
$$Gain = e^{b*Density}$$
$$log(Gain) = b*Density$$
using the data, the model with coefficients is
$$log(Gain) = b*Density + a + \epsilon$$

,where $b = -4.60594$ and $a = 5.99727$. 

If apply exponent
$$Gain = e^{b*Density + a} = e^{b*Density} *e^{a}$$

# Predict the Density using the models


```{r}
# without error term
# predict Gains using model1
#G.pred1 = exp(predict(model1, df1, level=0.95, interval="confidence"))

# but we want density, inverse estimating... using the equation of the model
D.pred1 = (log(df1$Gain) - model1$coefficients[1]) /  model1$coefficients[2]
# notice that they give the same point estimates of density

num = (D.pred1 - mean(df1$Gain))^2
denom = sum((df1$Gain - mean(df1$Gain))^2)

n = nrow(df1)
s.hat = 0.06792 # is this value right?
lowerb = D.pred1-(qnorm(0.975)*s.hat*sqrt((1/n) + num/denom))
upperb = D.pred1+(qnorm(0.975)*s.hat*sqrt((1/n) + num/denom))

lowerb < df1$Density & df1$Density < upperb
table(lowerb < df1$Density & df1$Density < upperb)


D.pred1.pt = (log(df1$Gain) - model1$coefficients[1] - model1$residuals) /  model1$coefficients[2]
lowerb.pt = D.pred1.pt - (qnorm(0.975)*s.hat*sqrt((1/n) + num/denom))
upperb.pt = D.pred1.pt + (qnorm(0.975)*s.hat*sqrt((1/n) + num/denom))
table(lowerb.pt < df1$Density & df1$Density < upperb.pt)
# with error term, all the interval estimates encompass all obs. densities

```



#plotting model1
$$Gain = c* e^{b*Density},$$
where $c = e^{a}$, $b = -4.60594$ and $a = 5.99727$.
\
```{r}

func = function(x){
  exp(model1$coefficients[2]*x)*exp(model1$coefficients[1])
}
dxg_df1
dxg_df1 + geom_function(fun =func) 
```



# modelling without extreme cases

## model2 - same as model1 but 0.001 density data removed from training set
```{r}
df2 = subset(df1, Density!= 0.001)
#model without 0.001
model2.l = lm(log(Gain)~Density, data=df2)
summary(model2.l)
coefs2.l = model2.l$coefficients
#plot(model2.l)

# but we want density
D.pred2.l = (log(df2$Gain) - model2.l$coefficients[1]) /  model2.l$coefficients[2]
# notice that they give the same point estimates of density

num2.l = (D.pred2.l - mean(df2$Gain))^2
denom2.l = sum((df2$Gain - mean(df2$Gain))^2)

n2.l = nrow(df2)
s.hat2.l = 0.0694 # is this value right?
lowerb2.l = D.pred2.l-(qnorm(0.975)*s.hat2.l*sqrt((1/n2.l) + num2.l/denom2.l))
upperb2.l = D.pred2.l+(qnorm(0.975)*s.hat2.l*sqrt((1/n2.l) + num2.l/denom2.l))

#check if observed density is within the interval
table(lowerb2.l < df2$Density & df2$Density < upperb2.l)


#predicting point est of density with error term
D.pred2.l.pt = (log(df2$Gain) - model2.b$coefficients[1] - model2.l$residuals) /  model2.b$coefficients[2]
lowerb2.l.pt = D.pred2.l.pt-(qnorm(0.975)*s.hat2.l*sqrt((1/n2.l) + num2.l/denom2.l))
upperb2.l.pt = D.pred2.l.pt+(qnorm(0.975)*s.hat2.l*sqrt((1/n2.l) + num2.l/denom2.l))

table(lowerb2.l.pt < df2$Density & df2$Density < upperb2.l.pt)

# with error term, all the interval estimates encompass all obs. densities

```
#model3 - same techniques as model1 but with 0.686 density data removed from training set
```{r}
df3 = subset(df1,  Density!= 0.686)
#model without 0.686
model2.u = lm(log(Gain)~Density, data=df3)
summary(model2.u)
coefs2.u = model2.u$coefficients
#plot(model2.u)

# but we want density
D.pred2.u = (log(df3$Gain) - model2.u$coefficients[1]) /  model2.u$coefficients[2]
# notice that they give the same point estimates of density

num2.u = (D.pred2.u - mean(df3$Gain))^2
denom2.u = sum((df3$Gain - mean(df3$Gain))^2)
n2.u = nrow(df3)
s.hat2.u = 0.06633 # is this value right?
lowerb2.u = D.pred2.u-(qnorm(0.975, nrow(df3)-2)*s.hat2.u*sqrt(1+ (1/n2.u) + num2.u/denom2.u))
upperb2.u = D.pred2.u+(qnorm(0.975, nrow(df3)-2)*s.hat2.u*sqrt(1+(1/n2.u) + num2.u/denom2.u))

lowerb2.u < df3$Density & df3$Density < upperb2.u
table(lowerb2.u < df3$Density & df3$Density < upperb2.u)

#predicting density with error term
D.pred2.u.pt=(log(df3$Gain) - model2.b$coefficients[1] - model2.u$residuals) /  model2.b$coefficients[2]
lowerb2.u.pt = D.pred2.u.pt-(qt(0.975, nrow(df3)-2)*s.hat2.u*sqrt(1+(1/n2.u) + num2.u/denom2.u))
upperb2.u.pt = D.pred2.u.pt+(qt(0.975, nrow(df3)-2)*s.hat2.u*sqrt(1+(1/n2.u) + num2.u/denom2.u))
table(lowerb2.u.pt < df3$Density & df3$Density < upperb2.u.pt)
# with error term, all the interval estimates encompass all obs. densities

```

#model4 - same techniques as model1 but both 0.001 0.686 density data removed from training set
```{r}
df4 = subset(df1,  Density>0.001 & Density<0.686)

#model without 0.686 and 0.001
model2.b = lm(log(Gain)~Density, data=df4)
summary(model2.b)
coefs2.b = model2.b$coefficients
#plot(model2.b)

# but we want density
D.pred2.b = (log(df4$Gain) - model2.b$coefficients[1]) /  model2.b$coefficients[2]



num2.b = (D.pred2.b - mean(df4$Gain))^2
denom2.b = sum((df4$Gain - mean(df4$Gain))^2)
n2.b = nrow(df4)
s.hat2.b = 0.06868 # is this value right?
lowerb2.b = D.pred2.b-(qt(0.975,df = nrow(df4)-2)*s.hat2.b*sqrt((1/n2.b) + num2.b/denom2.b))
upperb2.b = D.pred2.b+(qt(0.975, df = nrow(df4)-2)*s.hat2.b*sqrt((1/n2.b) + num2.b/denom2.b))

lowerb2.b < df4$Density & df4$Density < upperb2.b
table(lowerb2.b < df4$Density & df4$Density < upperb2.b)

#predicting density with error term
D.pred2.b.pt = (log(df4$Gain) - model2.b$coefficients[1] - model2.b$residuals) /  model2.b$coefficients[2]
lowerb2.b.pt = D.pred2.b.pt-(qnorm(0.975)*s.hat2.b*sqrt((1/n2.b) + num2.b/denom2.b))
upperb2.b.pt = D.pred2.b.pt+(qnorm(0.975)*s.hat2.b*sqrt((1/n2.b) + num2.b/denom2.b))
table(lowerb2.b.pt < df4$Density & df4$Density < upperb2.b.pt)
# with error term, all the interval estimates encompass all obs. densities

```

# error
truth = reported value + measurement error
```{r}
e= model1$residuals
qqnorm(e)
qqline(e)
shapiro.test(e)
# residuals are normally distributed
df1$Density 
```
# confidence interval of Density estimate by model
```{r}
# function to find lower and upper bounds for a model
CI = function(model, alpha){
  if(model == 1){
    num = (D.pred1 - mean(df1$Gain))^2
    denom = sum((df1$Gain - mean(df1$Gain))^2)
    n = nrow(df1)
    s.hat = 0.06792 # is this value right?
    lowerb = D.pred1-(qnorm(1-(alpha/2))*s.hat*sqrt((1/n) + num/denom))
    upperb = D.pred1+(qnorm(1-(alpha/2))*s.hat*sqrt((1/n) + num/denom))
  }
  else if(model==2){
    num2.l = (D.pred2.l - mean(df2$Gain))^2
    denom2.l = sum((df2$Gain - mean(df2$Gain))^2)
    n2.l = nrow(df2)
    s.hat2.l = 0.0694 # is this value right?
    lowerb = D.pred2.l-(qnorm(alpha/2)*s.hat2.l*sqrt((1/n2.l) + num2.l/denom2.l))
    upperb = D.pred2.l+(qnorm(alpha/2)*s.hat2.l*sqrt((1/n2.l) + num2.l/denom2.l))
  }
  else if(model==3){
    num2.u = (D.pred2.u - mean(df3$Gain))^2
    denom2.u = sum((df3$Gain - mean(df3$Gain))^2)
    n2.u = nrow(df3)
    s.hat2.u = 0.06633 # is this value right?
    lowerb = D.pred2.u-(qnorm(alpha/2)*s.hat2.u*sqrt((1/n2.u) + num2.u/denom2.u))
    upperb = D.pred2.u+(qnorm(alpha/2)*s.hat2.u*sqrt((1/n2.u) + num2.u/denom2.u))
  }
  else if(model==4){
    num2.b = (D.pred2.b - mean(df4$Gain))^2
    denom2.b = sum((df4$Gain - mean(df4$Gain))^2)
    n2.b = nrow(df4)
    s.hat2.b = 0.06868 # is this value right?
    lowerb = D.pred2.b-(qnorm(alpha/2)*s.hat2.b*sqrt((1/n2.b) + num2.b/denom2.b))
    upperb = D.pred2.b+(qnorm(alpha/2)*s.hat2.b*sqrt((1/n2.b) + num2.b/denom2.b))
  }
  else{
    print("model not found...")
    lowerb = NA
    upperb = NA
  }
  return(as.data.frame(cbind(lowerb,upperb)))
}

# 95% confidence interval of model1
CI(1,0.05)

# 95% confidence interval of model2.l 
# note: model2.l has log(Gain) as y and Density as x; data with low density:0.001 is removed 
CI(2,0.05)

# 95% confidence interval of model2.u
# note: model2.u has log(Gain) as y and Density as x; data with high density:0.686 is removed 
CI(3,0.05)

# 95% confidence interval of model2.b
# note: model2.b has log(Gain) as y and Density as x; both low density:0.001 and 0.686 are removed 
CI(4,0.05)
```

# Given a gain, what is it's estimated density and its interval, depending on the model used?
```{r}
estimateDensity = function(gain, model, alpha){
  if(model==1){
    pointEstimate = (log(gain) - model1$coefficients[1]) /  model1$coefficients[2]
    num = (pointEstimate - mean(df1$Gain))^2
    denom = sum((df1$Gain - mean(df1$Gain))^2)
    n = nrow(df1)
    s.hat = 0.06792 # is this value right?
    ci = pointEstimate + c(-1,1)*(qt(1-(alpha/2), nrow(df1)-2)*s.hat*sqrt(1+ (1/n) + num/denom))
  }
  else if(model==2){
    pointEstimate = (log(gain) - model2.l$coefficients[1]) /  model2.l$coefficients[2]
    num2.l = (pointEstimate - mean(df2$Gain))^2
    denom2.l = sum((df2$Gain - mean(df2$Gain))^2)
    n2.l = nrow(df2)
    s.hat2.l = 0.0694 # is this value right?
    ci = pointEstimate + c(-1,1)*(qt(1-(alpha/2), nrow(df2)-2)*s.hat2.l*sqrt(1+ (1/n2.l) + num2.l/denom2.l))
    
  }
  else if(model==3){
    pointEstimate = (log(gain) - model2.u$coefficients[1]) /  model2.u$coefficients[2]
    num2.u = (pointEstimate - mean(df3$Gain))^2
    denom2.u = sum((df3$Gain - mean(df3$Gain))^2)
    n2.u = nrow(df3)
    s.hat2.u = 0.06633 # is this value right?
    ci = pointEstimate + c(-1,1)*(qt(1-(alpha/2), nrow(df3)-2)*s.hat2.u*sqrt(1+ (1/n2.u) + num2.u/denom2.u))
  }
  else if(model==4){
    pointEstimate = (log(gain) - model2.b$coefficients[1]) /  model2.b$coefficients[2]
    num2.b = (pointEstimate - mean(df4$Gain))^2
    denom2.b = sum((df4$Gain - mean(df4$Gain))^2)
    n2.b = nrow(df4)
    s.hat2.b = 0.06868 # is this value right?
    ci = pointEstimate + c(-1,1)*(qt(1-(alpha/2), nrow(df4)-2)*s.hat2.b*sqrt(1+(1/n2.b) + num2.b/denom2.b))
    
  }
  else{
    print("model not found...")
    pointEstimate = NA
    ci = NA
  }
  
  df = data.frame(cbind(
    rep(c("point estimate ", "lowerb","upperb"),length(gain)),
    c(pointEstimate, ci)))
  names(df) = c("label", "value")
  return(df)
}
```


/plot the conf intervals for each model

```{r}
# put model type: 1,2,3,4, gains, fit.value of density and their, se.fit. in a df then add on the plot

m1 = rep(1, length(D.pred1))
m2 = rep(2, length(D.pred2.l))
m3 = rep(3, length(D.pred2.u))
m4 = rep(4, length(D.pred2.b))
model = c(m1,m2,m3,m4)
p.estimates = c(D.pred1, D.pred2.l, D.pred2.u, D.pred2.b)
est.df = data.frame(model,p.estimates)

func = function(x){
  exp(model1$coefficients[2]*x)*exp(model1$coefficients[1])
}
dxg_df1
dxg_df1 + geom_function(fun =func) 
```


